---
title: "Untitled"
author: "Tian Sun"
date: "2023-03-03"
output:
  powerpoint_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(dplyr)
library(readr)
library(ggplot2)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Test
```{r, results = FALSE, message=FALSE}
    data_wrfu_streaming_completed_part01 <- read_csv("data-wrfu-streaming-completed-part01.csv")
    data_wrfu_streaming_completed_part02 <- read_csv("data-wrfu-streaming-completed-part02.csv")
    wrfu <- rbind(data_wrfu_streaming_completed_part01, data_wrfu_streaming_completed_part02)
    wrfu$continent_code <- ifelse(wrfu$continent_name == "North America", "NA", wrfu$continent_code)
```

NA Rate
```{r}
    length(which(apply(wrfu, 1, function(X) any(is.na(X)))))/nrow(wrfu)
```
## World Wide Distribution
```{r}
    a <- na.omit(wrfu)
    a$Date<-with(a,paste(`end time of listener session year`, `end time of listener session month`, `end time of listener session day`,sep="-"))
    b <- a %>% 
      group_by(continent_name) %>% 
      summarise(count = n()) %>% 
      arrange(desc(count))
    print(as.data.frame(b))
```

## World Wide Distribution
```{r, out.width = '75%', fig.align = 'center'}
    length(unique(a$masked_ip))

    c <- a %>% 
      select(continent_name, continent_code, masked_ip) %>% 
      distinct(masked_ip, .keep_all = TRUE) %>% 
      group_by(continent_name) %>% 
      summarise(count = n()) %>% 
      arrange(desc(count))
    print(as.data.frame(c))
    
    p <- ggplot(c, aes(x=continent_name, y=count, fill=continent_name)) +
      geom_bar(stat="identity")+
      geom_text(aes(label=count), vjust=-0.3, size=3.5)+
      theme_minimal()
    p
```

## Special EU Listener "2705.093"
```{r}
    d <- a %>% 
      filter(continent_code == "EU") %>% 
      filter(masked_ip == 2705.093) %>% 
      select(`minutes of overlap between listen time and show time`, `total minutes of listen time`, Date, `end time of listener session time`, `end time of listener session year`, `show title`, continent_code, continent_name, masked_ip)
    print(as.data.frame(d))
    nrow(d)
```

## Most Popular Show
```{r}
    e <- a %>% 
      filter(`minutes of overlap between listen time and show time` >= 1) %>% 
      group_by(`show title`) %>% 
      summarise(count = n()) %>% 
      arrange(desc(count))
    e
    
    f <- a %>% 
      filter(`minutes of overlap between listen time and show time` >= 1) %>% 
      group_by(`show title`, `end time of listener session year`) %>% 
      summarise(count_by_year = n()) %>% 
      ungroup(`end time of listener session year`) %>% 
      mutate(count = sum(count_by_year)) %>% 
      filter(`show title`%in%(e$`show title`[1:6]))
    f
    
    f$`end time of listener session year`<- as.factor(f$`end time of listener session year`)
    
    ggplot(data=f, aes(x=`show title`, y=count_by_year, fill=`end time of listener session year`)) +
      geom_bar(position="dodge", stat="identity")+
      geom_text(aes(label=count_by_year), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5)+
      theme_minimal()
```
